PhD Title \\ PhD Thesis

### 2024-06-25 Latex_files/Thesis/chapters/chapter 3/main.tex
updates

\subsection{Position detection methods}
In order to accurately capture the dynamics of a trapped particle, 
a position detection system must be utilised. While possible to characterise
an optical trap using a linear position detector
A QPD is a typical example of a position detection system commonly used 
in optical tweezers due to their high sampling rate, high degree of 
precision, and ease of set up. The QPD is constructed of four photo 
diodes assembled in a quadrant formation, when a particle is trapped the 
interference pattern produced is directed onto the QPD, with the maximum 
intensity mapping to the particle's centre of mass. By summing the 
horizontal and vertical quadrants together the particle's centre of mass 
is tracked in the x-y plane. While the tracking is accurate the QPD 
needs to be calibrated in order to convert the voltage signals into 
actual distance reading.

>>>>

\subsection{Position detection methods}
In order to accurately capture the dynamics of a trapped particle, 
a position detection system must be utilised. There are 3 possible
methods of position detection: video-analysis, lateral-effect
position sensing, and quadrant photodiodes. The former being 
ideally suited for multiple traps or situations where precision
is not the top priority. In order to match the force measurements
of back-focal plane interferometry requires the camera's frame
rate to exceed $1\ kHz$ which can be difficult to achieve while 
maintaining a decent resolution \cite{Gibson2008}. In comparison
off the shelf back-focal plane detectors can achieve temporal
resolutions anywhere from $10-100\ kHz$.

A QPD is frequently used position detection system for optical 
tweezers due to their high sampling rate, high degree of 
precision, and ease of set up. The QPD is constructed of four photo 
diodes assembled in a quadrant formation, when a particle is trapped the 
interference pattern produced is focused onto the QPD, with 
the maximum intensity mapping to the particle's centre of mass. 
By summing the voltages of the horizontal and vertical quadrants 
together the particle's centre of mass is tracked in the x-y 
plane. Axial displacement can be estimated by observing the change
in the total voltage of the QPD. The outputted signal gives an
indication of the particle's relative displacement from the beam 
focus, but in order to convert the signal to distance units the
trap needs to be calibrated (assuming a linear response curve).

A lateral-effect sensor has a similar output but works using a 
the entire photodiode as a single cell. The four corners of 
the sensor act as anodes connected to a base plate cathode, as 
the beam moves across the surface of the detector the 4 corners
detect a photocurrent and
